Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-04 mr-review.Rmd
added more ref

A two-stage statistical model involves two regression models [@burgess_review_2017]. For a continuous 
outcome, one may choose to perform "two-stage least squares", which involves two linear regressions. 
First, the exposure variable is regressed on the instrument (*i.e.*, the SNP genotypes) (Equation \@ref(eq:lm1)). The resulting 
fitted values for the exposure variable are the independent variable in the second linear regression, 
where the outcome variable is the dependent variable. The causal effect estimate, then, is the 
coefficient obtained from the second regression analysis.

@@

Recognition of the many ways that the MR assumptions may be violated has inspired methods advances that 
enable assumption relaxations under certain conditions and has motivated use of sensitivity analysis to quantify the impact of possible assumption violations.

@@

Recognition of complex traits' diverse genetic architectures has fueled development of two-sample MR methods with multiple instruments [@Boyle2017].

>>>>

A two-stage statistical model involves two regression models [@burgess_review_2017]. For a continuous 
outcome, one may choose to perform "two-stage least squares", which involves two linear regressions. 
First, the exposure variable is regressed on the instrument (*i.e.*, the SNP genotypes) (Equation \@ref(eq:lm1)). The resulting 
fitted values for the exposure variable are the independent variable in the second linear regression, 
where the outcome variable is the dependent variable. The causal effect estimate, then, is the 
coefficient $\hat \beta_1$ obtained from the second regression analysis (Equation \@ref(eq:lm2)).

@@

Recognition of the many ways that the MR assumptions may be violated has inspired methods advances that 
enable assumption relaxations and has motivated use of sensitivity analysis to quantify the impact of 
possible assumption violations.

@@

Recognition of complex traits' diverse genetic architectures has fueled development of two-sample MR methods with multiple instruments [@hormozdiari_leveraging_2018;@watanabe_global_2019].
